Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
converting footnote urls to bib entries; working on the text a little

\category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]
\category{D.2.7}{Software Engineering}{Distribution, Maintenance, and Enhancement}[Version control]

@@

\keywords{Maven Repository, JDepend, Software Metrics, Chidamber and Kemerer.}

@@

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al. \cite{LOKI94} that have found their way in software development practice and tools. Today a software engineer or developer has a very large list of metrics at her disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.

@@

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.

@@

\section{On the Use of Domain Specific Languages}
\label{sec:dsl}

>>>>

\category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]

@@

\keywords{JDepend, Software Metrics, Chidamber and Kemerer.}

@@

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al. \cite{LOKI94} that have found their way in software development practice and tools.

@@

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)} \cite{CKJMDDS} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.

@@

\section{Experimenting with the Dataset}
\label{sec:dsl}
